---
title: "Lab 2"
author: "Collin Loy, Michelle Cryder"
date: "September 13, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Loading Data

```{r}

choco <- read.csv("https://ds202-at-isu.github.io/labs/data/choco.csv")
head(choco)

```

## Question Set Team

1. What is the overall number of chocolate bars rated?

1852 Chocolate bars

2. How does the number of ratings depend on the year? Draw a bar chart of the number of reports
  + The amount of ratings seems to be on a fairly stead increase until after 2015 when you see a major drop off.

```{r}

library(ggplot2)

choco <- read.csv("https://ds202-at-isu.github.io/labs/data/choco.csv")


count = c()
k = 1
for (i in 2006 : 2017){
  count[k] = sum(choco$Review.Date == i)
  k = k + 1
}

year = c(2006 : 2017)

DataYear = cbind(year, count)


ggplot(aes(x = year), data = as.data.frame(DataYear)) +
  geom_bar(aes(weight= count)) 


```
<br>

## Question set (individual)


3. For each of the questions below  provide at least one graphic as a basis for your answer.
    1. How are ratings distributed? Draw a histogram of ratings and describe it. Don't forget to mention outliers, if there are any.
        + There is almost a  normal distribution, but slightly skewed left.
    
```{r}
ggplot(choco, aes(x = Rating)) + geom_histogram(binwidth = 0.25) + ggtitle("Ratings Distribution") + xlab("Rating") + ylab("Count")

```
<br>    
    
  2. Do ratings depend on the cocoa percentage of a chocolate bar? 
      + No correlation
      + Though cocoa percentage doesnt seem to affect rating; some countries seem to have different preferences for the amount in there chocolate.
```{r}

ggplot(data = choco, aes(x = Cocoa.Pct, y = Rating)) + geom_jitter() + ggtitle("Cocoa Percentage vs Rating") + xlab("Cocoa %") + ylab("Rating")

top3 <- dplyr::filter(choco, Company.Location %in% c("U.S.A.", "France", "Canada"))

ggplot(data = top3, aes(x = Cocoa.Pct, y = Company.Location)) + geom_jitter() + ggtitle("Cocoa Percentage vs Rating") + xlab("Cocoa %") + ylab("Rating")


```
<br> 

  3. How do ratings compare across different company locations? Focus on the three locations with the most ratings:
      + Similar medians, Canada has a higher pecentage with higher ratings.
      + Outliers for USA and France torward the Lower end of the scale and france seems to have less ratings below 2.5 than the other countries.
    
```{r, message=FALSE}
top3 <- dplyr::filter(choco, Company.Location %in% c("U.S.A.", "France", "Canada"))
ggplot(data = top3, aes(x = Company.Location, y = Rating)) + geom_boxplot() + coord_flip() + ggtitle("Company Location Ratings") + ylab("Rating") + xlab("Company Location")

```

<br>

## Your own question? (team)

1. Discuss a question you want to investigate.
  + We decided to look deeper into which of the top three countries and which had a higher cocoa percentage in there chocolate. 

<br>

2. Answer this question by graphs.
  
```{r}
ggplot(top3, aes(x = Cocoa.Pct)) + geom_histogram(binwidth = 5, bins=20) + ggtitle("Cocoa Percentage Distribution") + facet_wrap(~Company.Location) + xlab("Cocoa %") + ylab("Count")

ggplot(top3, aes(x = Cocoa.Pct, fill=Company.Location)) + geom_histogram(binwidth = 5, bins=20) + ggtitle("Cocoa Percentage Distribution") + xlab("Cocoa %") + ylab("Count")

ggplot(data = top3, aes(x = Cocoa.Pct, y = Rating, colour=Company.Location)) + geom_jitter() + ggtitle("Cocoa Percentage vs Rating") + xlab("Cocoa %") + ylab("Rating")

#ggplot(data = top3, aes(x = Company.Location, y = Cocoa.Pct)) + geom_boxplot() + coord_flip() + ggtitle("Cocoa Percentage by Location") + ylab("Cocoa %") + xlab("Company Location")

ggplot(data = top3, aes(x = reorder(Company.Location, Cocoa.Pct, FUN=median), y = Cocoa.Pct)) + geom_boxplot() + coord_flip() + ggtitle("Cocoa Percentage by Location") + ylab("Cocoa %") + xlab("Company Location")


```

3. Conclusions.
  + The graphs we created show that France seems to have a higher median for cocoa percentage than hte USA and Canada; whos medians are nearly equal
  + This helps confirm what we saw when comparing Ratings vs Cocoa Percentage that though it has little affect on ratings; different countries shows different preferences.
  
  
## Paragraph and githublink

click [here](https://github.com/loycollin/Lab2-loycollin/blob/master/Lab2.Rmd) for the github link

Workflow:
  
  When we started in the lab work flow and communication was simple and straight forward as we just followed the questions and discussed ways to  complete the work, but this changed as we got out of class. Most of us as students are used to working in groups but with coding sometimes chages made can be less obvious so we communicated through social media and left comments via github; well both doing what we could. Overall I would say that the workflow was still fairly smooth, but for more complex assignments in the future; better detailed notes on github about coding changes may be a good change to make; as we discuss what to do through other communication platforms.


Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
